---
title: "CNP heatmap"
author: "Abby Lewis"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(akima)
library(colorRamps)
library(lubridate)

on <- as.Date(c("2019-06-03", "2019-07-08", "2019-08-05", "2019-09-02", "2021-06-11","2021-07-12","2021-07-26","2021-09-14"))
off <- as.Date(c("2019-06-17", "2019-07-18", "2019-08-19", NA,"2021-06-26","2021-07-14","2021-09-06",NA))
on_off = data.frame(on,off,Reservoir="FCR")%>%
  mutate(Year = year(on))
```

DOC
```{r}
#Load data
chem <- read_csv('../data/clean_data/chemistry.csv')
doc_2021 <- read_csv("../data/clean_data/2021_TOC_collation.csv")%>%
  mutate(DateTime = as.POSIXct(DateTime,format = "%m/%d/%y %H:%M"))%>%
  select(-DIC_mgL, -DC_mgL)

chem = chem%>%
  full_join(doc_2021)

#Create a dataset for just this variable
doc_fcr_2019 <- chem%>%filter(!is.na(DOC_mgL),
                    Depth_m<=9.3,
                    Reservoir == "FCR",
                    Site == 50,
                    DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))%>%
  mutate(DateTime = as.Date(DateTime),
         Year = year(DateTime))

doc_fcr_2021 <- chem%>%filter(!is.na(DOC_mgL),
                    Depth_m<=9.3,
                    Reservoir == "FCR",
                    Site == 50,
                    DateTime>as.Date("2021-06-01")&DateTime<as.Date("2021-11-01"))%>%
  mutate(DateTime = as.Date(DateTime),
         Year = year(DateTime))

doc_bvr_2019 <- chem%>%filter(!is.na(DOC_mgL),
                    Depth_m<=11,
                    Reservoir == "BVR",
                    Site == 50,
                    DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))%>%
  mutate(DateTime = as.Date(DateTime),
         Year = year(DateTime))

doc_bvr_2021 <- chem%>%filter(!is.na(DOC_mgL),
                    Depth_m<=11,
                    Reservoir == "BVR",
                    Site == 50,
                    DateTime>as.Date("2021-06-01")&DateTime<as.Date("2021-11-01"))%>%
  mutate(DateTime = as.Date(DateTime),
         Year = year(DateTime))

#Interpolate to get values at all depths and dates
doc_fcr_2019_interp <- interp2xyz(interp(doc_fcr_2019$DateTime,doc_fcr_2019$Depth_m,doc_fcr_2019$DOC_mgL,xo = seq(min(doc_fcr_2019$DateTime), max(doc_fcr_2019$DateTime), .5),yo = seq(min(doc_fcr_2019$Depth_m), max(doc_fcr_2019$Depth_m), by = .01)),data.frame = T)

doc_fcr_2021_interp <- interp2xyz(interp(doc_fcr_2021$DateTime,doc_fcr_2021$Depth_m,doc_fcr_2021$DOC_mgL,xo = seq(min(doc_fcr_2021$DateTime), max(doc_fcr_2021$DateTime), .5),yo = seq(min(doc_fcr_2021$Depth_m), max(doc_fcr_2021$Depth_m), by = .01)),data.frame = T)

doc_bvr_2019_interp <- interp2xyz(interp(doc_bvr_2019$DateTime,doc_bvr_2019$Depth_m,doc_bvr_2019$DOC_mgL,xo = seq(min(doc_bvr_2019$DateTime), max(doc_bvr_2019$DateTime), .5),yo = seq(min(doc_bvr_2019$Depth_m), max(doc_bvr_2019$Depth_m), by = .01)),data.frame = T)

doc_bvr_2021_interp <- interp2xyz(interp(doc_bvr_2021$DateTime,doc_bvr_2021$Depth_m,doc_bvr_2021$DOC_mgL,xo = seq(min(doc_bvr_2021$DateTime), max(doc_bvr_2021$DateTime), .5),yo = seq(min(doc_bvr_2021$Depth_m), max(doc_bvr_2021$Depth_m), by = .01)),data.frame = T)

#DOC heatmap
jpeg("../figures/DOC_heatmap_2019_2021.jpeg",width = 8, height = 4, units = "in", res = 300)
doc_fcr_2019_interp%>%
  full_join(doc_fcr_2021_interp)%>%
  mutate(Reservoir = "FCR")%>%
  full_join(doc_bvr_2019_interp%>%mutate(Reservoir="BVR"))%>%
  full_join(doc_bvr_2021_interp%>%mutate(Reservoir="BVR"))%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  ggplot(aes(x=x, y=y))+
  geom_raster(aes(fill = z))+
  scale_y_reverse(expand = c(0,0))+
  labs(x = "", y = "Depth (m)", title = "Dissolved Organic Carbon",fill=expression('(mg/L)'))+
  scale_fill_gradientn(colours = blue2green2red(100), na.value="gray")+
  geom_point(data = doc_fcr_2019, aes(x=DateTime, y=0.2), size = .2, fill = "white")+
  geom_point(data = doc_bvr_2019, aes(x=DateTime, y=0.2), size = .2, fill = "white")+
  geom_point(data = doc_fcr_2021, aes(x=DateTime, y=0.2), size = .2, fill = "white")+
  geom_point(data = doc_bvr_2021, aes(x=DateTime, y=0.2), size = .2, fill = "white")+
  geom_vline(aes(xintercept = on), data= on_off)+
  geom_vline(aes(xintercept = off),lty=2, data = on_off)+
  geom_text(aes(x = off+1, y = 1, label = "off", hjust = 0),data = on_off)+
  geom_text(aes(x = on+1, y = 1, label = "on", hjust = 0),data = on_off)+
  scale_x_date(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA))+
  facet_grid(rows= vars(Reservoir),
             cols = vars(Year),
             scales = "free",
             space = "free_x")
dev.off()
```
Iron
```{r}
#Load data
inUrl1  <- "https://pasta-s.lternet.edu/package/data/eml/edi/718/2/57912981e3e857c85924484806492446" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

                   
 metals <-read.csv(infile1,header=F 
          ,skip=1
            ,sep=","  
        , col.names=c(
                    "Reservoir",     
                    "Site",     
                    "DateTime",     
                    "Depth_m",     
                    "TFe_mgL",     
                    "TMn_mgL",     
                    "SFe_mgL",     
                    "SMn_mgL",     
                    "Flag_DateTime",     
                    "Flag_TFe",     
                    "Flag_TMn",     
                    "Flag_SFe",     
                    "Flag_SMn"    ), check.names=TRUE)
               
unlink(infile1)

#Create a dataset for just this variable
fe_fcr_2019 <- metals%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"),
         Year = 2019)%>%
  filter(!is.na(TFe_mgL),
         Depth_m<=9.3,
         Reservoir == "FCR",
         Site == 50,
         DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))

fe_fcr_2021 <- metals%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"),
         Year = 2021)%>%
  filter(!is.na(TFe_mgL),
         Depth_m<=9.3,
         Reservoir == "FCR",
         Site == 50,
         DateTime>as.Date("2021-06-01")&DateTime<as.Date("2021-11-01"))

fe_bvr_2019 <- metals%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"),
         Year = 2019)%>%
  filter(!is.na(TFe_mgL),
         Depth_m<=11,
         Reservoir == "BVR",
         Site == 50,
         DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))

fe_bvr_2021 <- metals%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"),
         Year = 2021)%>%
  filter(!is.na(TFe_mgL),
         Depth_m<=11,
         Reservoir == "BVR",
         Site == 50,
         DateTime>=as.Date("2021-05-31")&DateTime<as.Date("2021-11-01"))

#Interpolate to get values at all depths and dates
fe_fcr_2019_interp <- interp2xyz(interp(fe_fcr_2019$DateTime,fe_fcr_2019$Depth_m,fe_fcr_2019$TFe_mgL,xo = seq(min(fe_fcr_2019$DateTime), max(fe_fcr_2019$DateTime), .5),yo = seq(min(fe_fcr_2019$Depth_m), max(fe_fcr_2019$Depth_m), by = .01)),data.frame = T)

fe_fcr_2021_interp <- interp2xyz(interp(fe_fcr_2021$DateTime,fe_fcr_2021$Depth_m,fe_fcr_2021$TFe_mgL,xo = seq(min(fe_fcr_2021$DateTime), max(fe_fcr_2021$DateTime), .5),yo = seq(min(fe_fcr_2021$Depth_m), max(fe_fcr_2021$Depth_m), by = .01), duplicate = "mean"),data.frame = T)

fe_bvr_2019_interp <- interp2xyz(interp(fe_bvr_2019$DateTime,fe_bvr_2019$Depth_m,fe_bvr_2019$TFe_mgL,xo = seq(min(fe_bvr_2019$DateTime), max(fe_bvr_2019$DateTime), .5),yo = seq(min(fe_bvr_2019$Depth_m), max(fe_bvr_2019$Depth_m), by = .01)),data.frame = T)

fe_bvr_2021_interp <- interp2xyz(interp(fe_bvr_2021$DateTime,fe_bvr_2021$Depth_m,fe_bvr_2021$TFe_mgL,xo = seq(min(fe_bvr_2021$DateTime), max(fe_bvr_2021$DateTime), .5),yo = seq(min(fe_bvr_2021$Depth_m), max(fe_bvr_2021$Depth_m), by = .01)),data.frame = T)

#Fe heatmap
jpeg("../figures/Fe_heatmap_2019_2021.jpeg",width = 8, height = 4, units = "in", res = 300)
fe_fcr_2019_interp%>%
  full_join(fe_fcr_2021_interp)%>%
  mutate(Reservoir = "FCR")%>%
  full_join(fe_bvr_2019_interp%>%mutate(Reservoir="BVR"))%>%
  full_join(fe_bvr_2021_interp%>%mutate(Reservoir="BVR"))%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  ggplot(aes(x=x, y=y))+
  geom_raster(aes(fill = z))+
  scale_y_reverse(expand = c(0,0))+
  labs(x = "", y = "Depth (m)", title = "Total Iron ",fill=expression('(mg/L)'))+
  scale_fill_gradientn(colours = blue2green2red(100), na.value="gray")+
  geom_point(data = fe_fcr_2019, aes(x=DateTime, y=0.2), size = .2, color = "white")+
  geom_point(data = fe_bvr_2019, aes(x=DateTime, y=0.2), size = .2, color = "white")+
  geom_point(data = fe_fcr_2021, aes(x=DateTime, y=0.2), size = .2, color = "white")+
  geom_point(data = fe_bvr_2021, aes(x=DateTime, y=0.2), size = .2, color = "white")+
  geom_vline(aes(xintercept = on), data= on_off, color = "white")+
  geom_vline(aes(xintercept = off),lty=2, data = on_off, color = "white")+
  geom_text(aes(x = off+1, y = 1, label = "off", hjust = 0),data = on_off, color = "white")+
  geom_text(aes(x = on+1, y = 1, label = "on", hjust = 0),data = on_off, color = "white")+
  scale_x_date(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA))+
  facet_grid(rows= vars(Reservoir),
             cols = vars(Year),
             scales = "free",
             space = "free_x")
dev.off()
```
Oxygen
```{r}
#Load data
do <- read.csv('../data/clean_data/CTD_2013_2021.csv')
do = do%>%
  mutate(Date = as.Date(Date))%>%
  filter(!is.na(DO_mgL),
         Site == 50,
         (Date>as.Date("2019-06-01")&Date<as.Date("2019-11-01"))|
           (Date>=as.Date("2021-03-01")&Date<as.Date("2021-12-01")),
         Date != as.Date("2019-07-18")|Reservoir=="FCR")
#Trim dataset
depths <- seq(0,11, by = .1)
newDepths <- depths
df.final<- do %>% group_by(Date, Reservoir) %>% slice(which.min(abs(as.numeric(Depth_m) - depths[1]))) #Create a new dataframe
df.final$Depth_m <- newDepths[1]
for (i in 2:length(depths)){ #loop through all depths and add the closest values to the final dataframe
  ctd_atThisDepth <- do %>% group_by(Date, Reservoir) %>% slice(which.min(abs(as.numeric(Depth_m) - depths[i])))
  ctd_atThisDepth$Depth_m <- newDepths[i]
  df.final <- rbind(df.final,ctd_atThisDepth)
}

inUrl2  <- "https://pasta.lternet.edu/package/data/eml/edi/198/9/b3bd353312f9e37ca392e2a5315cc9da" 
infile2 <- tempfile()
try(download.file(inUrl2,infile2,method="curl"))
if (is.na(file.size(infile2))) download.file(inUrl2,infile2,method="auto")

                   
 ysi <-read.csv(infile2,header=F 
          ,skip=1
            ,sep=","  
        , col.names=c(
                    "Reservoir",     
                    "Site",     
                    "DateTime",     
                    "Depth_m",     
                    "Temp_C",     
                    "DO_mgL",     
                    "DOSat",     
                    "Cond_uScm",     
                    "Sp_cond_uScm",     
                    "PAR_umolm2s",     
                    "ORP_mV",     
                    "pH",     
                    "Flag_DateTime",     
                    "Flag_Temp",     
                    "Flag_DO",     
                    "Flag_DOSat",     
                    "Flag_Cond",     
                    "Flag_Sp_Cond",     
                    "Flag_PAR",     
                    "Flag_ORP",     
                    "Flag_pH"    ), check.names=TRUE)
               
unlink(infile2)

ysi%>%
  mutate(Date = as.Date(DateTime))%>%
  filter(year(Date)==2021,
         Reservoir=="BVR",
         Depth_m == 9)

df.final2 = df.final%>%
  full_join(ysi%>%select("Reservoir",     
                    "Site",     
                    "DateTime",     
                    "Depth_m",  
                    "DO_mgL")%>%
              filter(!is.na(DO_mgL))%>%
              mutate(Date = as.Date(DateTime))%>%
              filter(Date>=as.Date("2021-07-26"),
                     Date<as.Date("2021-12-01"))
              )


#Create a dataset for just this variable
do_fcr_2019 <- df.final2%>%
  mutate(Year = year(Date))%>%
  filter(Year == 2019,
         Reservoir == "FCR",
         Depth_m <= 9.3)

do_fcr_2021 <- df.final2%>%
  mutate(Year = year(Date))%>%
  filter(Year == 2021,
         Reservoir == "FCR",
         Depth_m <= 9.3)

do_bvr_2019 <- df.final2%>%
  mutate(Year = year(Date))%>%
  filter(Year == 2019,
         Reservoir == "BVR",
         Depth_m <= 11)

do_bvr_2021 <- df.final2%>%
  mutate(Year = year(Date))%>%
  filter(Year == 2021,
         Reservoir == "BVR",
         Depth_m <= 11)

#Interpolate to get values at all depths and dates
do_fcr_2019_interp <- interp2xyz(interp(do_fcr_2019$Date,do_fcr_2019$Depth_m,do_fcr_2019$DO_mgL,xo = seq(min(do_fcr_2019$Date), max(do_fcr_2019$Date),1 ),yo = seq(min(do_fcr_2019$Depth_m), max(do_fcr_2019$Depth_m), by = .01), duplicate = "mean"),data.frame = T)

do_fcr_2021_interp <- interp2xyz(interp(do_fcr_2021$Date,do_fcr_2021$Depth_m,do_fcr_2021$DO_mgL,xo = seq(min(do_fcr_2021$Date), max(do_fcr_2021$Date),1 ),yo = seq(min(do_fcr_2021$Depth_m), max(do_fcr_2021$Depth_m), by = .01), duplicate = "mean"),data.frame = T)

do_bvr_2019_interp <- interp2xyz(interp(do_bvr_2019$Date,do_bvr_2019$Depth_m,do_bvr_2019$DO_mgL,xo = seq(min(do_bvr_2019$Date), max(do_bvr_2019$Date), 1),yo = seq(min(do_bvr_2019$Depth_m), max(do_bvr_2019$Depth_m), by = .01), duplicate = "mean"),data.frame = T)

do_bvr_2021_interp <- interp2xyz(interp(do_bvr_2021$Date,do_bvr_2021$Depth_m,do_bvr_2021$DO_mgL,xo = seq(min(do_bvr_2021$Date), max(do_bvr_2021$Date), 1),yo = seq(min(do_bvr_2021$Depth_m), max(do_bvr_2021$Depth_m), by = .01), duplicate = "mean"),data.frame = T)

#DO heatmap
jpeg("../figures/DO_heatmap_2019_2021.jpeg",width = 8, height = 4, units = "in", res = 300)
do_fcr_2019_interp%>%
  full_join(do_fcr_2021_interp)%>%
  mutate(Reservoir = "FCR")%>%
  full_join(do_bvr_2019_interp%>%mutate(Reservoir="BVR"))%>%
  full_join(do_bvr_2021_interp%>%mutate(Reservoir="BVR"))%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  ggplot(aes(x=x, y=y))+
  geom_raster(aes(fill = z))+
  scale_y_reverse(expand = c(0,0))+
  labs(x = "", y = "Depth (m)", title = "Dissolved Oxygen ",fill=expression('(mg/L)'))+
  scale_fill_gradientn(colours = rev(blue2green2red(100)), na.value="gray")+
  geom_point(data = do_fcr_2019, aes(x=Date, y=0.2), size = .2, fill = "white")+
  geom_point(data = do_bvr_2019, aes(x=Date, y=0.2), size = .2, fill = "white")+
  geom_point(data = do_fcr_2021, aes(x=Date, y=0.2), size = .2, fill = "white")+
  geom_point(data = do_bvr_2021, aes(x=Date, y=0.2), size = .2, fill = "white")+
  geom_vline(aes(xintercept = on), data= on_off)+
  geom_text(aes(x = off+1, y = 1, label = "off", hjust = 0),data = on_off)+
  geom_text(aes(x = on+1, y = 1, label = "on", hjust = 0),data = on_off)+
  geom_vline(aes(xintercept = off),lty=2, data = on_off)+
  scale_x_date(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA))+
  facet_grid(rows= vars(Reservoir),
             cols = vars(Year),
             scales = "free",
             space = "free_x")
dev.off()
```

Simple metals graph (shows metals concentrations are only high when DO is very low)
```{r}
metals_lowest = metals%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"))%>%
  filter(Site == 50, 
         DateTime>as.Date("2021-06-01")&DateTime<as.Date("2021-11-01")|
           DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))%>%
  group_by(Reservoir, DateTime)%>%
  filter(Depth_m == max(Depth_m))

metals_lowest_comb = metals_lowest%>%
  left_join(df.final2%>%mutate(DateTime = as.Date(Date)))

metals_lowest_comb%>%
  ggplot(aes(y = TFe_mgL, x = DO_mgL, color = Reservoir))+
  geom_point()
```

Simple DOC graph (shows no clear relationship between oxygen and DOC)
```{r}
doc_lowest = chem%>%
  mutate(DateTime = as.Date(DateTime, format = "%m/%d/%Y %H:%M"))%>%
  filter(Reservoir %in% c("FCR","BVR"),
         Site == 50, 
         DateTime>as.Date("2021-06-01")&DateTime<as.Date("2021-11-01")|
           DateTime>as.Date("2019-06-01")&DateTime<as.Date("2019-11-01"))%>%
  group_by(Reservoir, DateTime)%>%
  filter(Depth_m == max(Depth_m))

doc_lowest%>%
  left_join(df.final2%>%mutate(DateTime = as.Date(Date)))%>%
  ggplot(aes(y = DOC_mgL, x = DO_mgL, color = Reservoir))+
  geom_point()

doc_lowest%>%
  ggplot(aes(x = DateTime,y=DOC_mgL,color = Reservoir))+
  geom_point()
```

Simple FeOC graph (shows no clear relationship between DO and FeOC)
```{r}
feoc = read.csv("../data/processed_data/reservoir_feoc.csv")
feoc$Reservoir[feoc$Reservoir=="f"]<-"FCR"
feoc$Reservoir[feoc$Reservoir=="b"]<-"BVR"


#Goal: trim DO dataset to get a DO value at 9m (FCR) or 11 m (BVR) on the closest date
new_do = df.final2 %>% filter(Reservoir=="FAKE") #Create a new dataframe
for(Res in c("FCR","BVR")){
  for(dates in unique(feoc$Date_collected[feoc$Reservoir==Res])){
    if(Res=="FCR"){Depth=9}else{Depth=11}
    closest_cast = df.final2 %>% 
      ungroup()%>%
      filter(Reservoir==Res, Depth_m==Depth)%>%
      mutate(Date_reflected = dates,
             Dist = abs(Date-as.Date(dates)))%>%
      slice(which.min(Dist))
    new_do <- rbind(new_do,closest_cast)
  }
}

dt1 = feoc%>%
  filter(!Sed_trap, Fe_OC_pct>0)%>%
  mutate(DateTime = as.Date(Date_collected))%>%
  left_join(new_do%>%mutate(DateTime=as.Date(Date_reflected)))

dt1%>%
  ggplot(aes(x = DO_mgL, y = Fe_OC_pct, color = Reservoir))+
  geom_point()+
  facet_wrap(~Reservoir)

summary(lm(Fe_OC_pct~DO_mgL, data=dt1%>%filter(Reservoir=="FCR")))
```


FeOC vs # of hypoxic days (using interpolated DO data)
- Significant negative relationship in FCR (as expected! Driven mainly by differences between years)
- Note than carbon pct increases with anoxia (due to mineralization?)
- Significant positive relationship per unit sed (rather than per unit OC). Because Fe is lost changing sed mass?
```{r}
interp_do = do_fcr_2019_interp%>%
  full_join(do_fcr_2021_interp)%>%
  mutate(Reservoir = "FCR")%>%
  full_join(do_bvr_2019_interp%>%mutate(Reservoir="BVR"))%>%
  full_join(do_bvr_2021_interp%>%mutate(Reservoir="BVR"))%>%
  mutate(DateTime = as.Date(x, origin = "1970-01-01"))


new_do = interp_do %>% filter(Reservoir=="FAKE") #Create a new dataframe
for(Res in c("FCR","BVR")){
  for(dates in as.Date(c(min(interp_do$DateTime):max(interp_do$DateTime[year(interp_do$DateTime)==2019]),
                 min(interp_do$DateTime[year(interp_do$DateTime)==2021]):max(interp_do$DateTime)), 
                 origin = "1970-01-01")){
    if(Res=="FCR"){Depth=9}else{Depth=11}
    closest_cast = interp_do %>% 
      filter(Reservoir==Res, y==Depth)%>%
      mutate(Date_reflected = as.Date(dates, origin = "1970-01-01"),
             Dist = as.Date(dates, origin = "1970-01-01")-DateTime)%>%
      slice(which(Dist<150&Dist>=0))%>%
      group_by(Reservoir,Date_reflected)%>%
      summarize(n = n(),
        anoxic_days = sum(z<2))
    new_do <- rbind(new_do,closest_cast)
  }
}

new_do%>%
  mutate(Date_reflected=as.Date(Date_reflected))%>%
  ggplot(aes(x = Date_reflected,y=anoxic_days, color = Reservoir))+
  geom_line()

feoc%>%
  filter(!Sed_trap)%>%
  mutate(DateTime = as.Date(Date_collected))%>%
  left_join(new_do%>%mutate(DateTime=as.Date(Date_reflected)))%>%
  ggplot(aes(x = anoxic_days, y = Fe_OC_pct, color = Reservoir, shape = as.factor(year(DateTime))))+
  geom_point()+
  facet_wrap(~Reservoir)

feoc%>%
  filter(!Sed_trap)%>%
  mutate(DateTime = as.Date(Date_collected))%>%
  left_join(new_do%>%mutate(DateTime=as.Date(Date_reflected)))%>%
  ggplot(aes(x = anoxic_days, y = C_pct_init, color = Reservoir, shape = as.factor(year(DateTime))))+
  geom_point()+
  facet_wrap(~Reservoir)

feoc%>%
  filter(!Sed_trap)%>%
  mutate(DateTime = as.Date(Date_collected))%>%
  left_join(new_do%>%mutate(DateTime=as.Date(Date_reflected)))%>%
  ggplot(aes(x = anoxic_days, y = Fe_OC_per_unit_sed, color = Reservoir, shape = as.factor(year(DateTime))))+
  geom_point()+
  facet_wrap(~Reservoir)

feoc_fcr=feoc%>%
  filter(!Sed_trap)%>%
  mutate(DateTime = as.Date(Date_collected))%>%
  left_join(new_do%>%mutate(DateTime=as.Date(Date_reflected)))%>%
  filter(Reservoir=="FCR")

summary(lm(feoc_fcr$Fe_OC_pct~feoc_fcr$anoxic_days))
summary(lm(feoc_fcr$Fe_OC_per_unit_sed~feoc_fcr$anoxic_days))
summary(lm(feoc_fcr$C_pct_init~feoc_fcr$anoxic_days))

```

Using oxygen exposure time for Fe and DOC separately
```{r}
new_do = interp_do %>% filter(Reservoir=="FAKE") #Create a new dataframe
for(Res in c("FCR","BVR")){
  for(dates in as.Date(c(min(interp_do$DateTime):max(interp_do$DateTime[year(interp_do$DateTime)==2019]),
                 min(interp_do$DateTime[year(interp_do$DateTime)==2021]):max(interp_do$DateTime)), 
                 origin = "1970-01-01")){
    if(Res=="FCR"){Depth=9}else{Depth=11}
    closest_cast = interp_do %>% 
      filter(Reservoir==Res, y==Depth)%>%
      mutate(Date_reflected = as.Date(dates, origin = "1970-01-01"),
             Dist = as.Date(dates, origin = "1970-01-01")-DateTime)%>%
      slice(which(Dist<150&Dist>=0))%>%
      group_by(Reservoir,Date_reflected)%>%
      summarize(n = n(),
        anoxic_days = sum(z<1))
    new_do <- rbind(new_do,closest_cast)
  }
}

metals_fcr = metals_lowest%>%
  left_join(new_do%>%mutate(DateTime = as.Date(Date_reflected)))

metals_fcr%>%
  ggplot(aes(y = TFe_mgL, x = anoxic_days, color = Reservoir))+
  geom_point()+
  facet_wrap(~Reservoir)

summary(lm(metals_fcr$TFe_mgL~metals_fcr$anoxic_days))

doc_fcr = doc_lowest%>%
  left_join(new_do%>%mutate(DateTime = as.Date(Date_reflected)))

doc_fcr%>%
  ggplot(aes(y = DOC_mgL, x = anoxic_days, color = Reservoir))+
  geom_point()+
  facet_wrap(~Reservoir)

summary(lm(doc_fcr$DOC_mgL~doc_fcr$anoxic_days))
```

