---
title: "Incubations: aqueous samples"
author: "Abby Lewis"
date: "9/22/2021"
output: html_document
---

This code chunk creates a graph of dissolved oxygen, dissolved organic carbon, total and soluble Fe in water samples over the course of the 34-day microcosm incubations. It takes as input three data files (organic carbon, iron, and dissolved oxygen) and produces one graph (combined_exp_graph_full.jpg)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(egg)

#Load data
oc = read.csv("../data/processed_data/TOC_formatted.csv") #Organic carbon data
fe = read.csv("../data/processed_data/acidified_Fe_formatted.csv") #Iron data 
do = read.csv("../data/processed_data/DO_formatted.csv")  #Dissolved oxygen and pH data

#Combine datasets
full = oc%>%
  full_join(fe, by = c("Treatment", "Sample_day", "Rep", "filt"))%>%
  full_join(do, by = c("Treatment", "Sample_day", "Rep"))%>%
  mutate(Status = ifelse(Treatment %in% c("Anoxic","Anoxic to oxic"),"Anoxic","Oxic"))

#Before the 13th day of the experiment, there was no difference between the anoxic to oxic microcosms and the anoxic microcosms
full$Treatment[full$Treatment=="Anoxic to oxic"&full$Sample_day<=13]<-"Hypoxic"
#Before the 13th day of the experiment, there was no difference between the oxic to anoxic microcosms and the oxic microcosms
full$Treatment[full$Treatment=="Oxic to anoxic"&full$Sample_day<=13]<-"Oxic"
full$Treatment[full$Treatment=="Oxic to anoxic"]<-"Oxic to hypoxic"
full$Treatment[full$Treatment=="Anoxic to oxic"]<-"Hypoxic to oxic"
full$Treatment[full$Treatment=="Anoxic"]<-"Hypoxic"

#Create descriptive names for the variables that will be plotted as facets
facets = c("DOC (mg/L)", "Dissolved Fe (mg/L)","Total Fe (mg/L)","DO (mg/L)")
names(facets) = c("NPOC_mgL", "Filtered","Unfiltered","DO_mgL")

#Iron includes both filtered and unfiltered samples that are currently grouped in one column (Conc). The code below separates these samples into two columns for plotting
formatted = full%>%
  mutate(Iron = Calculated_Fe_conc_ugL/1000)%>% #convert to mg/L
  pivot_wider(names_from = filt,
              values_from = c(Iron))%>%
  pivot_longer(cols = c(NPOC_mgL, Unfiltered,Filtered,DO_mgL))%>%
  filter(!is.na(Status))

formatted$name <- factor(formatted$name, levels = c("DO_mgL", "NPOC_mgL", "Unfiltered", "Filtered")) #Order the variables how we would like them to be plotted

#Create graph
do_graph = formatted%>%
  filter(name=="DO_mgL")%>%
  ggplot(aes(x = Sample_day, y = value, color = Treatment))+
  geom_point(size=1)+
  ylab("DO (mg/L)")+
  xlab("Day of experiment")+
  geom_vline(xintercept = 13.5)+
  scale_color_manual(values = c("#175676","#D58936","#A44200","#4BA3C3")) +
  facet_wrap(~Status)+
  theme_bw()+
  theme(strip.text.x = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        plot.margin = unit(c(5.5, 5.5, 1, 5.5), "pt"))

doc = formatted%>%
  filter(name=="NPOC_mgL")%>%
  ggplot(aes(x = Sample_day, y = value, color = Treatment))+
  geom_point(size=1)+
  ylab("DOC (mg/L)")+
  xlab("Day of experiment")+
  geom_vline(xintercept = 13.5)+
  scale_color_manual(values = c("#175676","#D58936","#A44200","#4BA3C3")) +
  facet_wrap(~Status)+
  theme_bw()+
  theme(strip.text.x = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        plot.margin = unit(c(1, 5.5, 1, 5.5), "pt"))

fe = formatted%>%
  filter(name=="Unfiltered")%>%
  ggplot(aes(x = Sample_day, y = value, color = Treatment))+
  geom_point(size=1)+
  ylab("Total Fe (mg/L)")+
  xlab("Day of experiment")+
  geom_vline(xintercept = 13.5)+
  scale_color_manual(values = c("#175676","#D58936","#A44200","#4BA3C3")) +
  facet_wrap(~Status)+
  theme_bw()+
  theme(strip.text.x = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        plot.margin = unit(c(1, 5.5, 1, 5.5), "pt"))

sfe = formatted%>%
  filter(name=="Filtered")%>%
  ggplot(aes(x = Sample_day, y = value, color = Treatment))+
  geom_point(size=1)+
  ylab("Dissolved Fe (mg/L)")+
  xlab("Day of experiment")+
  geom_vline(xintercept = 13.5)+
  scale_color_manual(values = c("#175676","#D58936","#A44200","#4BA3C3")) +
  facet_wrap(~Status)+
  theme_bw()+
  theme(strip.text.x = element_blank(),
        legend.position = "bottom",
        plot.margin = unit(c(1, 5.5, 0, 5.5), "pt"),
        legend.text = element_text(size = rel(1)),
        legend.text.align = 0)+
  guides(color = guide_legend(title = "Treatment: "))

#Save plot
jpeg("../figures/combined_exp_graph_full.jpg", width = 6, height = 6, units = "in",res = 300)
egg::ggarrange(do_graph,doc,fe,sfe, nrow = 4)
dev.off()

jpeg("../figures/total_vs_soluble_OC.jpg", width = 4, height = 4, units = "in",res = 300)
oc%>%
  mutate(Status = ifelse(Treatment %in% c("Anoxic","Anoxic to oxic"),"Anoxic","Oxic"))%>%
  pivot_wider(id_cols = c(Sample_day,Treatment,Status, Rep), names_from = filt, values_from = NPOC_mgL)%>%
  ggplot(aes(x = Filtered, y = Unfiltered))+
  geom_point()+
  xlab("Filtered water (dissolved organic carbon; mg/L)")+
  ylab("Unfiltered water (total organic carbon; mg/L)")+
  geom_smooth(method = "lm")+
  ylim(c(2.5,13))+
  xlim(c(2.5,13))+
  stat_regline_equation(aes(label =  paste(..eq.label..,..rr.label.., sep = "~~~~")))+
  geom_abline(slope = 1)+
  theme_bw()
dev.off()

calc = oc%>%
  mutate(Status = ifelse(Treatment %in% c("Anoxic","Anoxic to oxic"),"Anoxic","Oxic"))%>%
  pivot_wider(id_cols = c(Sample_day,Treatment,Status, Rep), names_from = filt, values_from = NPOC_mgL)%>%
  mutate(pct = Filtered/Unfiltered*100)
mean(calc$pct, na.rm = T)
sd(calc$pct, na.rm = T)

jpeg("../figures/incubation_pH.jpg", width = 6, height = 4, units = "in",res = 300)
#Before the 13th day of the experiment, there was no difference between the oxic to anoxic microcosms and the oxic microcosms
do$Treatment[do$Treatment=="Anoxic to oxic"&do$Sample_day<=13]<-"Hypoxic"
do$Treatment[do$Treatment=="Oxic to anoxic"&do$Sample_day<=13]<-"Oxic"
do$Treatment[do$Treatment=="Oxic to anoxic"]<-"Oxic to hypoxic"
do$Treatment[do$Treatment=="Anoxic to oxic"]<-"Hypoxic to oxic"
do$Treatment[do$Treatment=="Anoxic"]<-"Hypoxic"
do%>%
  mutate(Status = ifelse(Treatment %in% c("Anoxic","Anoxic to oxic"),"Anoxic","Oxic"))%>%
  ggplot(aes(x = Sample_day, y = pH, color = Treatment))+
  geom_point()+
  geom_vline(xintercept = 13)+
  scale_color_manual(values = c("#175676","#D58936","#A44200","#4BA3C3"))+
  theme_bw()+
  ylab("pH")+
  xlab("Day of experiment")+ 
  facet_wrap(~Status)
dev.off()
```


This code chunk creates a graph of ICP data from the end of the experiment. It takes as input one data file and produces one output figure
```{r}
icp = read.csv("../data/processed_data/ICP_clean.csv")

g = icp%>%
  filter(filt == "Unfiltered")%>%
  mutate(day = as.factor(Sample_day))%>%
  ggplot(aes(x = Treatment, y = Value, color = day))+
  geom_point(alpha=0.5)+
  scale_color_discrete(name = "Day")+
  facet_wrap(~Element, scales = "free_y", ncol = 5)+
  theme_bw()+
  ylab("Concentration (µg/L)")
g

jpeg("../figures/ICP_unfilt.jpg", width = 6.5, height = 7, units = "in", res = 300)
g
dev.off()
```

