---
title: "Sediment Analysis"
author: "Abby Lewis"
date: "11/19/2019"
output: html_document
---

This code file processes all sediment data from whole-ecosystem experiments. It is necessary to run all code chunks in order.
Section 0: Load necessary packages
Section 1: Load and prepare sediment OC/Fe-OC data
Section 2: Sediment data analysis
Section 3: Comparison of sediment to sedimenting material (sed traps)
Section 4: 2019 FCR whole-ecosystem experiments
Section 5: FCR and BVR multiannual comparison


Section 0: Load necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(lubridate)
library(ggpubr)
```

Section 1: Load and prepare data
```{r}
#Load data
calcs_raw = read.csv("../data/processed_data/Reservoir_sediment.csv", na = c("","NA"))

calcs_trimmed = calcs_raw%>%
  mutate(Date_collected=as.Date(Date_collected))%>%
  filter(is.na(Date_collected)|
           !(Date_collected == as.Date("2019-09-02")&Rep%in%c(3,4)| #spilled
               Date_collected == as.Date("2019-07-08")&Rep%in%c(3)| #spilled
               Date_collected<=as.Date("2019-07-02")))%>% #I am omitting the first sampling day because it was in a different location, stored differently, and my notes say it should just be practice
  mutate(Extracted_sed_mg = Vial_with_sed_after_fumig_mg-Vial_mg,
         CN_mg = ifelse(CN_mg > Extracted_sed_mg&!is.na(Extracted_sed_mg), Extracted_sed_mg, CN_mg),#The mass used for CN cannot be greater than the extracted sediment mass
         Correction = (Extracted_sed_mg-Initial_sed_mg)/Extracted_sed_mg,
         Correction = ifelse(Type == "init",0,Correction),
         Corrected_CN_mg = CN_mg-(CN_mg*Correction),
         C_pct = 100*C_mg/Corrected_CN_mg)

calcs_res = calcs_trimmed%>%
  pivot_wider(id_cols = c(Rep, Reservoir, Date_collected, Sed_trap), values_from = C_pct, names_from = Type, names_prefix = "C_pct_")%>%
  mutate(Fe_OC_pct = (C_pct_con - C_pct_ext) / C_pct_init *100,
         Fe_OC_per_unit_sed = 1000000*(C_pct_con-C_pct_ext)/55.85/100)%>%
  select(-C_pct_con,-C_pct_ext)
```


Section 2: Sediment data analysis 
Formats data for subsequent sections reports summary statistics for whole ecosystem Fe-OC.
```{r}
#Fe-OC summary statistics (grouped by reservoir)
calcs_res%>%
  filter(!is.na(Fe_OC_pct)&Fe_OC_pct>0,
         Sed_trap==F)%>%
  group_by(Reservoir)%>%
  summarize(min = min(Fe_OC_pct),
            max = max(Fe_OC_pct),
            mean = mean(Fe_OC_pct),
            SD = sd(Fe_OC_pct),
            n = n())

#Fe-OC summary statistics (not grouped by reservoir)
calcs_res%>%
  filter(!is.na(Fe_OC_pct)&Fe_OC_pct>0,
         Sed_trap==F)%>%
  #group_by(Reservoir)%>%
  summarize(min = min(Fe_OC_pct),
            max = max(Fe_OC_pct),
            mean = mean(Fe_OC_pct),
            SD = sd(Fe_OC_pct),
            n = n())

#Fe-OC summary statistics (sed trap)
calcs_res%>%
  filter(Sed_trap,
         !is.na(Fe_OC_pct))%>%
  summarize(min = min(Fe_OC_pct),
            max = max(Fe_OC_pct),
            mean = mean(Fe_OC_pct),
            SD = sd(Fe_OC_pct),
            n = n())
```



Section 3: Comparison of sediment to sedimenting material (sed traps)
This section exports one figure (Sed_to_sed_trap_comparison_comb.jpg; Figure 3)
```{r}
#STATS

#Fe-OC
stats = calcs_res%>%
  filter(Fe_OC_pct>0)
t.test(stats$Fe_OC_pct[stats$Sed_trap],stats$Fe_OC_pct[stats$Sed_trap==F]) #p<0.001
t.test(stats$Fe_OC_per_unit_sed[stats$Sed_trap],stats$Fe_OC_per_unit_sed[stats$Sed_trap==F]) #p<0.001
#Sediment OC
stats = calcs_res #remake the stats dataset without filtering such that Fe_OC_pct is >0
t.test(stats$C_pct_init[stats$Sed_trap],stats$C_pct_init[stats$Sed_trap==F]) #p<0.001
stats = calcs_res%>%
  filter(Fe_OC_pct>0)
mass_lim = c(min(stats$Fe_OC_per_unit_sed, na.rm = T),max(stats$Fe_OC_per_unit_sed, na.rm = T))
c_lim = c(min(stats$C_pct_init, na.rm = T),max(stats$C_pct_init, na.rm = T))
pct_lim = c(min(stats$Fe_OC_pct, na.rm = T),max(stats$Fe_OC_pct, na.rm = T))

#PLOTS
#Below, I make three separate plots that then get combined and exported
pct = calcs_res%>%
  filter(Fe_OC_pct>0,
         !is.na(Reservoir))%>%
  mutate(year = as.factor(year(Date_collected)),
         Reservoir = ifelse(Reservoir == "f","FCR","BVR"))%>%
  ggplot(aes(x = Sed_trap, y = Fe_OC_pct))+
  geom_boxplot(outlier.shape = NA, aes(color = Reservoir))+
  geom_jitter(position=position_jitterdodge(dodge.width=0.75, jitter.width = 0.2),aes(group=Reservoir, color = Reservoir, shape = year))+
  ylab("Fe-OC (% sediment OC)")+
  geom_text(aes(x = 1.5, y = pct_lim[2]-1/10*(pct_lim[2]-pct_lim[1]), label = "***"), size = 6, vjust = 0.5)+
  scale_x_discrete(labels=c("TRUE" = "Sedimentation Trap", "FALSE" = "Sediment"))+
  scale_shape_manual(values = c(1,16))+
  theme_bw()+
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))+
  labs(shape = "Year")+
  scale_color_manual(values = c("#4B4E6D","#80B192"))

c = calcs_res%>%
  mutate(year = as.factor(year(Date_collected)),
         Reservoir = ifelse(Reservoir == "f","FCR","BVR"))%>%
  ggplot(aes(x = Sed_trap, y = C_pct_init))+
  geom_boxplot(outlier.shape = NA, aes(color = Reservoir))+
  geom_jitter(position=position_jitterdodge(dodge.width=0.75, jitter.width = 0.2),aes(group=Reservoir, color = Reservoir, shape = year))+
  geom_text(aes(x = 1.5, y = c_lim[2]-1/10*(c_lim[2]-c_lim[1]), label = "***"), size = 6, vjust = 0.5)+
  ylab("OC (% sediment mass)")+
  xlab("")+
  scale_x_discrete(labels=c("TRUE" = "Sedimentation Trap", "FALSE" = "Sediment"))+
  scale_shape_manual(values = c(1,16))+
  theme_bw()+
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))+
  labs(shape = "Year")+
  scale_color_manual(values = c("#4B4E6D","#80B192"))

tot = calcs_res%>%
  mutate(year = as.factor(year(Date_collected)),
         Reservoir = ifelse(Reservoir == "f","FCR","BVR"))%>%
  filter(Fe_OC_per_unit_sed>0)%>%
  ggplot(aes(x = Sed_trap, y = Fe_OC_per_unit_sed))+
  geom_boxplot(outlier.shape = NA, aes(color = Reservoir))+
  geom_jitter(position=position_jitterdodge(dodge.width=0.75, jitter.width = 0.2),aes(group=Reservoir, color = Reservoir, shape = year))+
  ylab("Fe-OC (µmol/g sediment)")+
  xlab("")+
  geom_text(aes(x = 1.5, y = mass_lim[2]-1/10*(mass_lim[2]-mass_lim[1]), label = "***"), size = 6, vjust = 0.5)+
  scale_x_discrete(labels=c("TRUE" = "Sedimentation Trap", "FALSE" = "Sediment"))+
  scale_shape_manual(values = c(1,16))+
  theme_bw()+
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))+
  labs(shape = "Year")+
  scale_color_manual(values = c("#4B4E6D","#80B192"))

jpeg("../figures/Sed_to_sed_trap_comparison_comb.jpg", width = 6, height = 4, units = "in", res = 300)
ggarrange(tot,c, pct, nrow = 1, ncol = 3, common.legend = T, legend = "bottom")
dev.off()
```



Section 4: 2019 FCR whole-ecosystem experiments
This section creates one figure (All_sed_data_2019.jpg; Figure 4) and reports statistics comparing sediment properities between oxygenated and non-oxygenated periods in 2019
```{r}
#Oxygenation intervals
on <- as.Date(c("2019-07-08", "2019-08-05","2019-09-02"))
off <- as.Date(c("2019-07-18", "2019-08-19",NA))
on_off = data.frame(on,off,Reservoir="FCR")%>%
  mutate(Year = year(on))
#Set global point size
point_size = 2


#STATS
stats = calcs_res%>%
  filter(Reservoir == "f", #Only analyzing 2019 data
         year(Date_collected)==2019)%>%
  #filter(Date_collected!= as.Date("2019-09-02"))%>%
  mutate(on_off = ifelse(Date_collected%in%as.Date(c("2019-07-08","2019-08-05","2019-09-02")), "off","on"))

t.test(stats$C_pct_init~stats$on_off)
t.test(stats$Fe_OC_per_unit_sed~stats$on_off)
t.test(stats$Fe_OC_pct~stats$on_off)


#PLOTS
#Below, I make six separate plots that then get combined and exported

#Calculate axis limits
mass_lim = c(min(stats$Fe_OC_per_unit_sed, na.rm = T),max(stats$Fe_OC_per_unit_sed, na.rm = T))
c_lim = c(min(stats$C_pct_init, na.rm = T),max(stats$C_pct_init, na.rm = T))
pct_lim = c(min(stats$Fe_OC_pct, na.rm = T),max(stats$Fe_OC_pct, na.rm = T))

#Carbon graph
c_pct = calcs_res%>%
  mutate(Year = year(Date_collected),
         on_off = ifelse(Date_collected%in%as.Date(c("2019-07-08","2019-08-05","2019-09-02")), "off","on"))%>%
  filter(Year == 2019, Reservoir == "f",
         !Sed_trap,
         #Date_collected<as.Date("2019-09-01")
         )%>%
  ggplot(aes(y = C_pct_init))+
  ylab("OC (% sediment mass)")+
  xlab("")+
  theme_bw()+
  #geom_rect(aes(xmin = on, xmax = off, ymin = c_lim[1], ymax = c_lim[2]), fill = "#A2C9FD",data= on_off)+
  geom_vline(aes(xintercept = on), data= on_off)+
  geom_vline(aes(xintercept = off),lty=2, data = on_off)+
  geom_text(aes(x = off+1, y = c_lim[1], label = "off", hjust = 0),data = on_off)+
  geom_text(aes(x = on+1, y = c_lim[1], label = "on", hjust = 0),data = on_off[1:2,])+
  geom_point(size = point_size, shape = 21, aes(fill = on_off,x = Date_collected))+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  theme(legend.position = "none")

#Fe-OC mass graph
feoc_total = calcs_res%>%
  mutate(Year = year(Date_collected),
         on_off = ifelse(Date_collected%in%as.Date(c("2019-07-08","2019-08-05","2019-09-02")), "off","on"))%>%
  filter(Year == 2019, Reservoir == "f",
         !Sed_trap,
         #Date_collected<as.Date("2019-09-01")
         )%>%
  ggplot(aes(x = Date_collected,y = Fe_OC_per_unit_sed))+
  ylab("Fe-OC (µmol/g sediment)")+
  xlab("")+
  theme_bw()+
  geom_vline(aes(xintercept = on), data= on_off)+
  geom_vline(aes(xintercept = off),lty=2, data = on_off)+
  geom_text(aes(x = off+1, y = mass_lim[1], label = "off", hjust = 0),data = on_off)+
  geom_text(aes(x = on[-3]+1, y = mass_lim[1], label = "on", hjust = 0),data = on_off[1:2,])+
  geom_point(size = point_size, shape = 21, aes(fill = on_off))+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  theme(legend.position = "none")

#Fe-OC (percent of sediment OC) graph
feoc_pct = calcs_res%>%
  mutate(Year = year(Date_collected),
         on_off = ifelse(Date_collected%in%as.Date(c("2019-07-08","2019-08-05","2019-09-02")), "off","on"))%>%
  filter(Year == 2019, Reservoir == "f",
         !Sed_trap,
         #Date_collected<as.Date("2019-09-01")
         )%>%
  ggplot(aes(x = Date_collected,y = Fe_OC_pct))+
  ylab("Fe-OC (% sediment OC)")+
  xlab("")+
  theme_bw()+
  geom_vline(aes(xintercept = on), data= on_off)+
  geom_vline(aes(xintercept = off),lty=2, data = on_off)+
  geom_text(aes(x = off+1, y = pct_lim[1], label = "off", hjust = 0),data = on_off)+
  geom_text(aes(x = on[-3]+1, y = pct_lim[1], label = "on", hjust = 0),data = on_off[1:2,])+
  geom_point(size = point_size, shape = 21, aes(fill = on_off))+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  theme(legend.position = "none")

#Summary figures to add
# Carbon
test_c = stats%>%
  ggplot(aes(x = on_off, y= C_pct_init))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(width = 0.1, shape = 21, aes(fill = as.factor(on_off)), size = point_size)+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  ylab("OC (% sediment mass)")+
  geom_text(aes(x = 1.5, y = c_lim[2], label = "**"), vjust = 1)+
  xlab("")+
  ylab("")+
  theme_bw()+
  theme(legend.position = "none")

#Fe-OC (percent)
test_pct = stats%>%
  ggplot(aes(x = on_off, y= Fe_OC_pct))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(width = 0.1, shape = 21, aes(fill = as.factor(on_off)), size = point_size)+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  ylab("Fe-OC (% sediment OC)")+
  geom_text(aes(x = 1.5, y = pct_lim[2], label = "n.s."), vjust = 0.5)+
  xlab("")+
  ylab("")+
  theme_bw()+
  theme(legend.position = "none")

#Fe-OC (mass)
test_tot = stats%>%
  ggplot(aes(x = on_off, y= Fe_OC_per_unit_sed))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(width = 0.1, shape = 21, aes(fill = as.factor(on_off)), size = point_size)+
  scale_fill_manual(values = c("#FEB9BD","#A2C9FD"))+
  ylab("Fe-OC (µmol/g sediment)")+
  geom_text(aes(x = 1.5, y = mass_lim[2], label = "*"), vjust = 1)+
  xlab("")+
  ylab("")+
  theme_bw()+
  theme(legend.position = "none")

#Export all panels as one figure
jpeg("../figures/All_sed_data_2019.jpg", width = 6, height = 7.5, units = "in", res = 300)
ggarrange(feoc_total,test_tot,
          c_pct,test_c,
          feoc_pct, test_pct, nrow = 3, ncol = 2, widths = c(1,0.5),
          labels = c("a",NA,"b",NA,"c",NA),
          label.y = 1.02)
dev.off()

calcs_res%>%
  filter(Date_collected==as.Date("2019-08-05"))
```



Section 5: FCR and BVR multiannual comparison (stats and figure)
This section exports one figure (All_sed_data_res_12May22.jpg; Figure 7) and reports statistics comparing 2019 and 2021 in Falling Creek Reservoir (FCR) and Beaverdam Reservoir (BVR).
```{r}
#STATS
stats = calcs_res%>%
  filter(!Sed_trap,
         Reservoir == "f",
         is.na(Fe_OC_pct)|Fe_OC_pct>0)

stats%>%
  mutate(Year = year(Date_collected))%>%
  group_by(Year)%>%
  summarize(sd_pct = sd(Fe_OC_pct, na.rm= T),
            sd_mass = sd(Fe_OC_per_unit_sed, na.rm = T),
            sc_c = sd(C_pct_init, na.rm = T))

stats = calcs_res%>%
  filter(!Sed_trap,
         Reservoir == "b",
         is.na(Fe_OC_pct)|Fe_OC_pct>0)

stats%>%
  mutate(Year = year(Date_collected))%>%
  group_by(Year)%>%
  summarize(sd_pct = sd(Fe_OC_pct, na.rm= T),
            sd_mass = sd(Fe_OC_per_unit_sed, na.rm = T),
            sc_c = sd(C_pct_init, na.rm = T))

#PLOTS
plot_lims = calcs_res%>%
  filter(is.na(Fe_OC_pct)|Fe_OC_pct>0,
         Sed_trap==F)
mass_lim = c(min(plot_lims$Fe_OC_per_unit_sed, na.rm = T),max(plot_lims$Fe_OC_per_unit_sed, na.rm = T))
pct_lim = c(min(plot_lims$Fe_OC_pct, na.rm = T),max(plot_lims$Fe_OC_pct, na.rm = T))
c_lim = c(min(plot_lims$C_pct_init, na.rm = T),max(plot_lims$C_pct_init, na.rm = T))

# FeOC (% of sediment OC) stats for graph
to_plot = calcs_res%>%
  filter(!is.na(Fe_OC_pct),
         Fe_OC_pct>0,
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")))

summary(aov(lm(to_plot$Fe_OC_pct~to_plot$res_year)))
TukeyHSD(aov(lm(to_plot$Fe_OC_pct~to_plot$res_year)))

labs = data.frame(res_year = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021"),
                  label = c("a","a","b","a")) #based on anova results above
#Make graph
feoc_pct = calcs_res%>%
  filter(!is.na(Fe_OC_pct),
         Fe_OC_pct>0,
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")),
         color = ifelse(res_year=="FCR 2019","blue","black"))%>%
  ggplot(aes(x = res_year, y = Fe_OC_pct))+
  geom_text(aes(y = pct_lim[2]+1/10*(pct_lim[2]-pct_lim[1]), x = res_year, label = label), data = labs)+
  scale_color_manual(values = c("#000000","#217DAB"))+
  geom_boxplot(outlier.shape = NA, aes(color = color))+
  ylab("Fe-OC (% of sediment OC)")+
  xlab("")+
  geom_jitter(width = 0.1,aes(color = color))+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
        axis.title.x = element_blank())

# OC stats for graph
to_plot = calcs_res%>%
  filter(!is.na(C_pct_init),
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")))

summary(aov(lm(to_plot$C_pct_init~to_plot$res_year)))
TukeyHSD(aov(lm(to_plot$C_pct_init~to_plot$res_year)))
labs = data.frame(res_year = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021"),
                  label = c("a","a","b","a")) #based on anova results above
#Make graph
c_pct = calcs_res%>%
  filter(!is.na(C_pct_init),
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")),
         color = ifelse(res_year=="FCR 2019","blue","black"))%>%
  ggplot(aes(x = res_year, y = C_pct_init))+
  geom_text(aes(y = c_lim[2]+1/10*(c_lim[2]-c_lim[1]), x = res_year, label = label), data = labs)+
  scale_color_manual(values = c("#000000","#217DAB"))+
  geom_boxplot(outlier.shape = NA, aes(color = color))+
  ylab("OC (% sediment mass)")+
  xlab("")+
  geom_jitter(width = 0.1,aes(color = color))+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
        axis.title.x = element_blank())

# FeOC (mass) stats for graph
to_plot = calcs_res%>%
  filter(!is.na(Fe_OC_per_unit_sed),
         Fe_OC_pct>0,
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")))
summary(aov(lm(to_plot$Fe_OC_per_unit_sed~to_plot$res_year)))
# Make graph
feoc_sed = calcs_res%>%
  filter(!is.na(Fe_OC_per_unit_sed),
         Fe_OC_pct>0,
         Sed_trap==F)%>%
  mutate(year = as.factor(year(Date_collected)),
         res_year = factor(paste(year,Reservoir), levels = c("2019 b", "2021 b","2019 f", "2021 f"), labels = c("BVR 2019","BVR 2021","FCR 2019","FCR 2021")),
         color = ifelse(res_year=="FCR 2019","blue","black"))%>%
  ggplot(aes(x = res_year, y = Fe_OC_per_unit_sed, color = color))+
  geom_text(aes(y = mass_lim[2]+1/10*(mass_lim[2]-mass_lim[1]), x = "FCR 2019", label = "n.s."), hjust = 1)+ #Based on stats above
  scale_color_manual(values = c("#000000","#217DAB"), labels = c("Hypoxic","Oxic"))+
  geom_boxplot(outlier.shape = NA)+
  ylab("Fe-OC (µmol/g sediment)")+
  xlab("")+
  geom_jitter(width=0.1,aes(group=year))+
  theme_bw()+
  labs(color = "Average oxygen status")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
        axis.title.x = element_blank())

#Combine figures
jpeg("../figures/All_sed_data_res_12May22.jpg", width =6, height =3.5, units = "in", res = 300)
ggarrange(feoc_sed,c_pct,feoc_pct, nrow = 1, common.legend = T, legend = "bottom", labels = "auto")
dev.off()
```